Parallel Global Optimization for Non-Convex Mixed-Integer Problems

### 2019-03-25 2019/RSD_Integer/RSD2019.tex

Используя схему редукции размерности с помощью развертки $y(x), x\in [0,1]$ можно сопоставить каждой вложенной задаче минимизации по $y$ одномерную задачу минимизации

Let us formulate a set of problems based on the problem (\ref{problem_i})
\begin{gather}\label{problem_is}
\min{\left\{ g_{m+1}^s(y):y\in D, \; g_i^s(y)\leq 0, \; 1 \leq i \leq m\right\}},\\
D=\left\{ a_i\leq y_i \leq b_i, \;  y_i \in R, \; i \notin J \right\}, \; s\in\{1,...,S\}.\nonumber 
\end{gather}
Each of these problems corresponds to the initial problem (\ref{problem_i}) with some combination of 
integer parameters. The number of problems $S$ will correspond to the number of all possible 
combinations of the integer parameters.

Using the dimensionality reduction scheme utilizing the evolvent $y(x)$ 
%based on the set of problems (\ref{problem_is}),
one can compose a united problem 
\begin{equation}\label{problem_is1}
\min \left\{g_{m+1}^s(y^s(x)): x \in [0,S], \; g_i^s(y^s(x)) \leq 0, \; 1 \leq i \leq m\right\},
\end{equation}
where the mapping $y^s(x)$ is formed on the basis of initial evolvent $y(x)$ as follows
\[
y^s(x)=y(x-s), \; x\in[s-1,s],\; s\in\{1,...,S\}.
\]
The functions $g_i^s(y^s(x))$ can have the breaks at the points $s\in \{1,...,S-1\}$, therefore, 
these points were considered as the punctured ones, the values of the objective function and 
constraints at these points remain undefined.

>>>>

Используя схему редукции размерности с помощью развертки $y(x), x\in [0,1]$ можно сопоставить каждой вложенной задаче минимизации по $y$ одномерную задачу минимизации
\[
 \min{\left\{ g_{m+1}(y(x),u_s):x \in [0,1], \; g_j(y(x),u_s)\leq 0, \; 1 \leq j \leq m\right\}}, s\in\{1,...,S\}.
\]

Рассмотрим теперь соответствие 
\[
Y(x)=y(x-E(x)), \; x\in[0,S],
\]
отображающее любую точку интервала [0,S] на область $D$ (обозначение $E(x)$ соответствует целой части числа $x$) и определим функции 
\[
g_j(x) = g_j(Y(x),u_{E(x)+1}), x\in[0,S],
\]
имеющие, вообще говоря, разрывы первого рода в целочисленных точках $x_i = i, 1\leq i \leq S-1$.
Используя введенные обозначения можно переформулировать исходную задачу как
\[
\min \left\{g_{m+1}(x): x \in [0,S], \; g_j(x) \leq 0, \; 1 \leq j \leq m\right\}.
\]
